%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%   ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Mrs. Jane Smith \\
Recruitment Officer \\
The Corporation \\
123 Pleasant Lane \\
City, State 12345} 

%----------------------------------------------------------------------------------------
%   YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Tim Sizemore \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
315 State Road \\ China Grove, NC 28023 \\ (980) 621-8398 % Your address and phone number
\end{center} 
\vfill

\signature{Tim Sizemore} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%   LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Mrs. Smith,} 
 
I am interested in the position of programmer in your software development 
department. I heard about the position through several Western Carolina Alumni
that work in the department, specifically, Herbert Hoover, Franklin Roosevelt, 
and Harry Truman.

Naturally, I am a recent graduate from Western Carolina and I am looking for 
employment that accentuates my education. Being able to work in a small group
with a large amount of creative freedom is my ideal work environment. The 
Corporation exceeds all my asperations. The Corporation not only offers a 
programming position I am intrigued by, but its standards for environmental 
sustainability and stance on human rights align perfectly with mine. As an 
employee, I can further the company's ambitions without moral conflict and 
develop or maintain legacy code to the highest possible standard. My previous 
projects, while receiving my education, were built from the ground, up and 
always within a group of two or more. This gives me significant experience with
paired programming techniques and delegating tasks among unique individuals as 
well as an immeasurable amount of time writing and debugging code. Did I mention
I have debugged a lot of code? I mean a ludicrous amount.

I look forward to meeting with you in person to further discuss how my abilities
can benefit The Corporation. I will contact you within two weeks to discuss my
continued interest. Or if you would like to contact me before that time, my cell
number is listed at the top of the page and my email address is timsized@yahoo.com.
I deeply appreciate the time spend reviewing my application thus far.

\closing{Sincerely,}


%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
