\documentclass{article}
\usepackage[margin=.75in]{geometry}
\usepackage{enumitem}

\begin{document}
\title{All About Me}
\author{Tim Sizemore}

\maketitle

\begin{enumerate}
\item \textbf{Sports}
    \begin{enumerate}
    \item Football
        \begin{enumerate}
        \item I am a Panthers fan but I think they should get rid of Ron Rivera.
        \item Shannon Sharpe is my favorite player.
        \item Mike Shanahan and Tony Dungy are tied as my favorite coaches.
        \end{enumerate}
    \item Basketball
        \begin{enumerate}
        \item My favorite college team is University of Kentucky, Go Wildcats!
              And sorry Western.
        \item I do not have a favorite pro team, but I do enjoy watching the NBA.
        \end{enumerate}
    \item Swimming
        \begin{enumerate}
        \item I swam for three years in high school.
        \item Michael Phelps has helped the sport significantly.
        \item Female swimmers will eventually be able to compete with males.
        \end{enumerate}
    \item Track \& Field
        \begin{enumerate}
        \item I pole vaulted for five years throughout middle school and high
              school. I still hold my high school height record of 13'.
        \item I am a fan of Lola Jones and her attempt at multiple sports and
              I wish her all the luck in the world at Sochi.
        \end{enumerate}
    \end{enumerate}
\item \textbf{Games (Digital \& Table Top)}
    \begin{itemize}
    \item Video Games
        \begin{itemize}
        \item Rogue-like
            \begin{enumerate}
            \item Tales of Maj'eyal
            \item Rogue Legacy
            \item Faster Than Light
            \end{enumerate}
        \item MOBA
            \begin{enumerate}
            \item League of Legends (Moved from this to DoTA.)
            \item DoTA 2
            \item Briefly played Smite during its beta run.
            \end{enumerate}
        \item RPG
            \begin{enumerate}
            \item The Elder Scrolls (Pretty much anything Bethseda makes.)
            \item I have played more than I care to list and enjoyed most of them.
            \end{enumerate}
        \end{itemize}
    \item Card Games
        \begin{enumerate}
        \item Munchkin
        \item 500Rummy
        \item Dominion
        \end{enumerate}
    \item Table Tops
        \begin{enumerate}
        \item Settlers of Catan
        \item Monopoly!
        \end{enumerate}
    \end{itemize}
\item \textbf{Literature}
    \begin{itemize}
    \item Non-Fiction
        \begin{itemize}
        \item \textit{The Fabric of the Cosmos} by Brian Greene
        \item \textit{The Hidden Reality} by Brian Greene
        \item \textit{Death by Black Hole: And Other Cosmic Quandaries} by
              Neil deGrasse Tyson
        \item \textit{A Briefer History of Time} by Stephen Hawking
        \item \textit{E=mc\textsuperscript{2}} by David Bodanis
        \item \textit{Cosmos} by Carl Sagan 
        \item \textit{Pale Blue Dot} by Carl Sagan 
        \end{itemize}
    \item Non-Fiction
        \begin{itemize}
        \item \textit{The Hitchhiker's Guide to the Galaxy Series} by Douglas
              Adams
            \begin{itemize}
            \item I consider myself a seasoned reader. There is not another
                  person, dead or alive, that could tell a satirical tragedy like
                  Adams. He was truly a wordsmith and the main reason I became
                  interested in physics. I frequently allude to his works and
                  would consider him my favorite author.
            \end{itemize}
        \item \textit{The Complete Circle Series} by Ted Dekker
        \item \textit{Tales of the Lifesong} by Greg Hamerton
        \item \textit{Ender's Games Series} \& \textit{Bean Quartet} by Orson
              Scott Card
            \begin{itemize}
            \item The \textit{Bean Quartet} is superb. As a series, it is
                  significantly better than the Ender's Series.
            \end{itemize}
        \item \textit{A Game of Thrones Series} by George R.R. Martin
        \end{itemize}
    \end{itemize}
\item \textbf{Schedule of Classes}
    \begin{itemize}
    \item Monday \& Wednesday \& Friday
        \begin{itemize}
        \item CS   496 08:00AM - 09:00AM
        \item MATH 340 10:10AM - 11:00AM
        \item ANTH 260 11:15AM - 12:05PM
        \item CS   352 01:25PM - 02:15PM
        \end{itemize}
    \item Tuesday \& Thursday
        \begin{itemize}
        \item MATH 270 11:00AM - 12:15PM
        \item HT   437 03:30PM - 04:45PM
        \end{itemize}
    \end{itemize}
\item \textbf{Schools I Have Attended}
    \begin{itemize}
    \item Paducah, Kentucky
        \begin{enumerate}
        \item Farley Elementary
        \end{enumerate}
    \item China Grove, North Carolina
        \begin{enumerate}
        \item Bostian Elementary
        \item China Grove Middle
        \end{enumerate}
    \item Kannapolis, North Carolina
        \begin{enumerate}
        \item Enochville Elementary
        \item Corriher Lipe Middle
        \item South Rowan High
        \item Jesse Carson High
        \end{enumerate}
    \item Salisbury, North Carolina
        \begin{enumerate}
        \item Catawba College
        \end{enumerate}
    \item Cullowhee, North Carolina
        \begin{enumerate}
        \item Western Carolina University
        \end{enumerate}
    \end{itemize}
\end{enumerate}

\end{document}
