\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\textheight=10in
\pagestyle{empty}
%\raggedbottom
\raggedright

%\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }}
\newcommand{\contact}[3]{
\vspace*{-8pt}
\begin{center}
{\LARGE \scshape {#1}}\\
#2 \lineunder 
#3
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}
\newcommand{\schoolwithcourses}[4]{
 \textbf{#1} #2 $\bullet$ #3\\ 
#4 $\bullet$  Selected Coursework:\\
\vspace*{5pt}
}
\newcommand{\school}[4]{
 \textbf{#1} #2 $\bullet$ #3\\ 
#4 \\
}
% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\vspace*{-44pt}

\contact{Timothy T. Sizemore}
{315 State Road, China Grove NC 28023}
{(980) 621-8398 $\bullet$ timsized@yahoo.com}

\header{Education}

\schoolwithcourses{Western Carolina University}{Cullowhee, NC}{Bachelor of Science in Computer Sci., 2014}
    {}
    \area{Computer Science}{Data Structures $\cdot$ Algorithms $\cdot$ Computer Networking
    $\cdot$ Operating Systems $\cdot$ Object Oriented Systems $\cdot$ Databases $\cdot$ Mobile Application Development 
    $\cdot$ Computer Graphics $\cdot$ Software Engineering $\cdot$ Software Development $\cdot$ Computer Organization}
	\area{Mathematics}{Multivariable Calculus $\cdot$ Statistics $\cdot$ Discrete Math $\cdot$ Logic}

\header{Work History}
\employer{WCU Office of Institutional Planning \&
Effectiveness}{2011-2014}{Technical Assistant}
	\begin{achievements}
	\item Wrote queries to collect statistical data on University population for
        in office use.
	\item Designed Python scripts to retrieve dynamically generated pdfs and
        spreadsheets.
	\item Developed a program used by the WCU English department that assists in
        their end of the year assessment.
	\item Assisted in the development of a webapp to assist in the automation of
        data requests in and out of office.
	\end{achievements}

\header{Notable Projects (github.com/tsized)}
    \begin{itemize}
    \item Paint Clone
        \begin{itemize}
        \item Programmed using Java.
        \item Developed all shape and brush logic using common design patterns.
        \item Created a GUI using Swing.
        \end{itemize}
	\item Cache Simulator
        \begin{itemize}
        \item Programmed using Python.
        \item Uni-processor capable of storing 32 bytes.
        \item Command line interface.
        \end{itemize}
	\item Circular Bounded Buffer
        \begin{itemize}
        \item Programmed using C.
        \item Entire project completed within kernel space.
        \item Allows inter-process communication. Essentially, pipe.
        \end{itemize}
	\item Ray Tracer
        \begin{itemize}
        \item Programmed using C++.
        \item Creates ray traced graphics in 3D space.
		\item Capable of rendering ambient, diffuse, and specular lighting properties.
        \end{itemize}
	\item Assessment Assist
		\begin{itemize}
		\item Programmed using VBA.
		\item Automated file distribution and data collection with analysis on
			rubrics.
		\item Intuitive Excel interface.
		\end{itemize}
	\item PiBot
		\begin{itemize}
		\item Programmed using mostly Python.
		\item Consists of a MVC Flask framework dynamic five page website, an API
              that abstracts hardware from software, and a robot that transmits
              video back through the website.
		\item PiBot uses object detection to avoid hazards by utilizing the camera
              and a sonar sensor.
		\end{itemize}
    \end{itemize}

\header{Skills}
\begin{achievements}
\item Proficiency in software development in Java, Python, C, C++, Assembly,
	Visual Basic, Android.
\item Familiarity with Regular Expressions, Threads, Sockets, Database Design,
	SQL, Django, Flask, \LaTeX
\item Familiarity with UNIX, GNU/Linux, Win32.
\end{achievements}

\end{document}
